%-------------------------
% Author : Gavin Holtzapple
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{etoolbox}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Gavin Holtzapple} \\ \vspace{1pt}
    \small 480-227-6930 $|$ \href{mailto:holtzapplegavin@gmail.com}{\underline{holtzapplegavin@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/gholtzap/}{\underline{linkedin.com/in/gholtzap}} $|$
    \href{https://gholtzap.vercel.app/}{\underline{gholtzap.vercel.app}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Arizona State University}{Tempe, AZ}
      {Bachelor of Science in Computer Science | GPA: 3.4}{Aug 2021 - May 2025}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
{CX Apprentice}{Oct. 2024 - Present}
{Coinbase}{Remote}
\resumeItemListStart
    \resumeItem{Analyzed customer feedback to identify  pain points, informing product enhancements and improving user satisfaction.}
     \resumeItem{Collaborated with cross-functional teams to translate customer insights into actionable product features.}
      \resumeItem{Developed comprehensive knowledge of Coinbase products, contributing to the optimization of the user experience.}
\resumeItemListEnd

\resumeSubheading
{Product Manager Intern}{Jun. 2024 - Aug. 2024}
{Walmart}{New York City, NY}
\resumeItemListStart
    \resumeItem{\textbf{Reduced avg transaction time by 44\%} by introducing bluetooth hardware \& optimizing software.}
    \resumeItem{Created a \textbf{Sentiment Analysis Library \& Scraper} in \textbf{Python} to track competitor's digital payment systems.}
    \resumeItem{Created Mural flows, Confluence docs, White papers, Figma mockups, and Powerpoints for Walmart [NDA].}
    \resumeItem{Invented an optimized QR code to \textbf{reduce Azure costs by 5\%} and minimize the API Payload.}
\resumeItemListEnd

\resumeSubheading
      {Software Engineer Intern}{Oct. 2023 -- May 2024}
      {Rockwell Automation }{Phoenix, AZ}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Full-Stack} solutions using \textbf{React}/ \textbf{Node.JS}, enabling efficient parsing of machine-generated data.}
        \resumeItem{Integrated \textbf{AWS} services including \textbf{EC2}, \textbf{DynamoDB}, \textbf{Lambda}, and \textbf{S3}, enhancing system scalability.}
        \resumeItem{Modernized test infrastructure by transitioning from \textbf{Protractor} to \textbf{Cypress} for improved test automation.}
    \resumeItemListEnd
    \resumeSubheading
      {Software Engineer Intern}{May 2023 -- Aug. 2023}
      {Cigna}{Philadelphia, PA}
      \resumeItemListStart
        \resumeItem{Developed \textbf{REST APIs} using \textbf{Java} and \textbf{Springboot} to retrieve prescription data from \textbf{MongoDB} databases.}
        \resumeItem{Developed \textbf{Full-Stack CRUD} interfaces using \textbf{React, Java, \& Openshift} to interact with prescription data.}
        \resumeItem{Created a \textbf{Full-Stack app} with \textbf{React} and \textbf{Node} to improve company data processes for non-technical users.}
      \resumeItemListEnd
      

    \resumeSubheading
      {Software Engineer Intern}{May 2022 -- Aug. 2022}
      {Voice Media Group}{Phoenix, AZ}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Full-Stack Applications} using \textbf{React} and \textbf{Node} to automate company QA processes, saving an estimated \textbf{\$60,000 per year} in expenses.}
        \resumeItem{Migrated \textbf{Full-Stack Javascript} \& \textbf{Node} applications to \textbf{Typescript}, modernizing company development tools.}
        \resumeItem{Improved company website \textbf{SEO, UI, and UX} by modernizing user-facing web pages.}
    \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant - Computer Science}{Jan. 2022 -- Present}
      {Arizona State University}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Taught concepts of \textbf{Java}, \textbf{Object-Oriented Programming, Data Structures}, and \textbf{Algorithms}.}
        \resumeItem{Directly lead over 2000 students to success by teaching computer science concepts and \textbf{Algorithm Design}.}
        \resumeItem{Created educational resources for students regarding commonly misunderstood programming concepts.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}


    \resumeSubHeadingListStart

    \resumeProjectHeading
          {\textbf{Solisa AI} $|$ \emph Typescript, Next.JS}{}
          \resumeItemListStart
            \resumeItem{Valued at \$4.0 million, Solisa is a CRM platform for health insurance agents.}
          \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{Echo Labs} $|$ \emph Typescript, Next.JS}{}
          \resumeItemListStart
            \resumeItem{Echo Labs is my student-run software consulting firm. We make software for SBA and mixed funds worth billions of dollars.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Scoop (Robinhood Hackathon Winner)} $|$ \emph Typescript, Javascript, React, Next, Git, Express, HTML, CSS}{}
          \resumeItemListStart
            \resumeItem{Developed a \textbf{Full-Stack Web App} using \textbf{React} and \textbf{Node} to detect and predict epidemics in the USA.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Kingston Investment Tools} $|$ \emph{Python, Flask, Javascript, Matplotlib, Pandas}}{}
          \resumeItemListStart
            \resumeItem{Automated \textbf{Python} investing strategies returning anywhere from \textbf{200\% - 442\%} over 5-year intervals.}
          \resumeItemListEnd


        
    \resumeSubHeadingListEnd
%-----------LEADERSHIP-----------
\section{Leadership}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Volunteer Firefighter} $|$ \emph{Phoenix Fire Department}}{}
          \resumeItemListStart
            \resumeItem{Volunteer firefighter for the City of Phoenix under Search/Rescue and Medical divisions.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Community Assistant (Residential Assistant)} $|$ \emph{Arizona State University}}{}
          \resumeItemListStart
            \resumeItem{First line of contact for crisis alleviation and professional guidance for thousands of ASU students. }
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Vice President} $|$ \emph{ASU Esports Association}}{}
          \resumeItemListStart
            \resumeItem{Vice president of ASU's largest club. Led and managed sponsorships and finances for 3,000 club members.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
