%-------------------------
% Author : Gavin Holtzapple
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{etoolbox}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Gavin Holtzapple} \\ \vspace{1pt}
    \small 480-227-6930 $|$ \href{mailto:gholtzap@asu.edu}{\underline{gholtzap@asu.edu}} $|$ 
    \href{https://www.linkedin.com/in/gholtzap/}{\underline{linkedin.com/in/gholtzap}} $|$
    \href{https://gholtzap.github.io/}{\underline{gholtzap.github.io}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Arizona State University}{Phoenix, AZ}
      {Bachelor of Science in Computer Science | GPA: 3.4}{Aug. 2021 -- May 2025}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
      {Software Engineer Intern}{Oct. 2023 -- Present}
      {Rockwell Automation }{Phoenix, AZ}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Full-Stack} solutions using \textbf{React}/ \textbf{Node.JS}, enabling efficient parsing of machine-generated data.}
        \resumeItem{Integrated \textbf{AWS} services including \textbf{EC2}, \textbf{DynamoDB}, \textbf{Lambda}, and \textbf{S3}, enhancing system scalability.}
        \resumeItem{Modernized test infrastructure by transitioning from \textbf{Protractor} to \textbf{Cypress} for improved test automation.}
    \resumeItemListEnd
    \resumeSubheading
      {Software Engineer Intern}{May 2023 -- Aug. 2023}
      {Cigna}{Philadelphia, PA}
      \resumeItemListStart
        \resumeItem{Developed \textbf{REST APIs} using \textbf{Java} and \textbf{Springboot} to retrieve prescription data from \textbf{MongoDB} databases.}
        \resumeItem{Developed \textbf{Full-Stack CRUD} interfaces using \textbf{React, Java, \& Openshift} to interact with prescription data.}
        \resumeItem{Created a \textbf{Full-Stack app} with \textbf{React} and \textbf{Node} to improve company data processes for non-technical users.}
      \resumeItemListEnd
      

    \resumeSubheading
      {Software Engineer Intern}{May 2022 -- Aug. 2022}
      {Voice Media Group}{Phoenix, AZ}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Full-Stack Applications} using \textbf{React} and \textbf{Node} to automate company QA processes, saving an estimated \textbf{\$60,000 per year} in expenses.}
        \resumeItem{Migrated \textbf{Full-Stack Javascript} \& \textbf{Node} applications to \textbf{Typescript}, modernizing company development tools.}
        \resumeItem{Improved company website \textbf{SEO, UI, and UX} by modernizing user-facing web pages.}
    \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant - Computer Science}{Jan. 2022 -- Present}
      {Arizona State University}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Taught concepts of \textbf{Java}, \textbf{Object-Oriented Programming, Data Structures}, and \textbf{Algorithms}.}
        \resumeItem{Directly lead over 2000 students to success by teaching computer science concepts and \textbf{Algorithm Design}.}
        \resumeItem{Created educational resources for students regarding commonly misunderstood programming concepts.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Kingston Investment Tools} $|$ \emph{Python, Flask, Javascript, Matplotlib, Pandas}}{}
          \resumeItemListStart
            \resumeItem{Automated \textbf{Python} investing strategies returning anywhere from \textbf{200\% - 442\%} over 5-year intervals.}
            \resumeItem{Created visualization tools using \textbf{Python} and \textbf{Matplotlib} for investors to analyze \& plan their strategies.}
            \resumeItem{Used \textbf{Python} to develop a fair market value calculator, watchlist visualizer, and custom index maker.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Theta} $|$ \emph Typescript, Javascript, Python, Tailwind CSS, React, Git}{}
          \resumeItemListStart
            \resumeItem{Developed a \textbf{Full-Stack React Web App} with \textbf{Typescript} that displays investment tools for end users.}
            \resumeItem{Uses a series of \textbf{Python} formulas to deliver forecasts for stock tickers and allocate weight to user's portfolios.}
            \resumeItem{Uses \textbf{Python} and \textbf{Matplotlib} to create and visualize custom user-defined stock indexes.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{Scoop (Robinhood Hackathon Winner)} $|$ \emph Typescript, Javascript, React, Next, Git, Express, HTML, CSS}{}
          \resumeItemListStart
            \resumeItem{Developed a \textbf{Full-Stack Web App} using \textbf{React} and \textbf{Node} to detect and predict epidemics in the USA.}
            \resumeItem{Analyzed \& Visualized user-submitted symptom data to determine spreading illnesses by Zipcode.}
            \resumeItem{Created an \textbf{API} with \textbf{Express} and storage with \textbf{MongoDB} to store and retrieve all necessary data.}
          \resumeItemListEnd

        
    \resumeSubHeadingListEnd



%
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Javascript, Python, Java, Typescript, SQL, Git, HTML, CSS} \\
     \textbf{Tools}{: React, Node, Flask, Next, Springboot, Openshift, Pandas, NumPy, Matplotlib} \\
    }}
 \end{itemize}


%-----------LEADERSHIP-----------
\section{Leadership}
\resumeSubHeadingListStart
     
        \resumeProjectHeading
            {\textbf{Residential Assistant} $|$ \emph{Arizona State University}}{}
            \resumeItemListStart
            \resumeItem{Directly responsible for the health and success of hundreds of honors \& engineering students in student housing.}
            \resumeItem{Responded to campus crises \& ensured safety of surrounding communities as needed.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Vice President} $|$ \emph{ASU Esports Association}}{}
          \resumeItemListStart
            \resumeItem{Lead \& managed over 3,000 club members while streamlining finances, logistics, \& sponsorships.}
          \resumeItemListEnd
\resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
